Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-09 paper/paper.tex
few edits

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
  }}
  \vspace{-3ex}
\end{figure}

@@

Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
three elements that we use to characterize a warning--1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

As it is the case for most empirical evaluations, our findings are
subject to internal, external, and construct validity
threats. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines. To
mitigate this threat, we carefully selected inputs from various
sources according to a well-defined criteria. Likewise, we selected
the engines by using using a well-defined criteria and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market. In
terms of construct validity, we used standard metrics to determine the
effectiveness of the testing techniques we studied (\eg{}, number of
bugs confirmed and fixed and severity). Engine developers were
responsible for determining the labels of the bug reports and their
severity. Consequently, these metrics originate from a trusted source.

>>>>

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 150 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 150 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

@@

\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
available in the \jsc codebase.  The \radamsa fuzzing technique
mutated the test. In particular, it introduced the negative
long \texttt{-1770523502845470856} as a parameter of the
\texttt{view.getInt8()} method. Before the mutation, the
\texttt{view.getInt8()} method received a zero integer.}
At the botom of this figure, there is a sequence of
three elements that we use to characterize a warning--1) the
identifier of an engine, 2) the exception it raises, and 3) the
message it produces on a ``\lo'' warning.  This sequence of triples
defines a warning signature that we use for clustering. It is worth
mentioning that we filter references to code in messages as to
increase ability to aggregate warnings. Any warnings, including this
one, that has this same signature will be included in the same
``bucket''. Considering the example from
Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
  bounds of the DataView'')].

@@

As it is the case for most empirical evaluations, our findings are
subject to internal, external, and construct validity
threats. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines. To
mitigate this threat, we carefully selected inputs from various
sources according to a well-defined criteria. Likewise, we selected
the engines by using using a well-defined criteria and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market.
\Fix{One reader might argue that since we mined files from other JS engines,
such as Duktape, JerryScript, JSI, and Tiny-js, we could also run test
transplantation on them. We did not run test transplantation on these
JS engines due to several reasons, including: JSI was deprecated,
TinyJS is not actively maintained. Finally, at the time we started this work,
Duktape and JerryScript did not provide support to ES6. We checked this
information again in Jun 2020, and they are still only partially supporting ES6.
}
In
terms of construct validity, we used standard metrics to determine the
effectiveness of the testing techniques we studied (\eg{}, number of
bugs confirmed and fixed and severity). Engine developers were
responsible for determining the labels of the bug reports and their
severity. Consequently, these metrics originate from a trusted source.
